### 2018-01-21 study-dataset.tex
minor fixes

Here, we use the GOF scores obtained by \citet{Taborda_2014_BSSA} independently of the velocity models and/or the component of motions. Although at times we will make distinctions between the models and the components for visualization purposes, the clustering analysis to be discussed next was done using the whole dataset of GOF scores. The motivation behind this choice was that the dataset, as a sample of GOF scores, was independent of the simulation and serves here as a generic set for the purpose of identifying the correlations that exist between the different metrics in Table \ref{tab:metrics}. As such, given the simulations for each velocity model (3), the components of motion (3), and the number of stations used in the validation (336) gives us a large enough sample. Figure \ref{fig:data-box-plot} reinforces precisely this idea by comparing the statistical distribution of the broadband GOF scores of the simulations classified by velocity models and components. It is clear that although there are differences between them, these are minor and negligible; in other words, the statistical distribution of results for each metric is about the same independently of model or component.

>>>>

Here, we use the GOF scores obtained by \citet{Taborda_2014_BSSA} independently of the velocity models and/or the component of motions. Although at times we will make distinctions between the models and the components for visualization purposes, the clustering analysis to be discussed next was done using the whole dataset of GOF scores. The motivation behind this choice was that the dataset, as a sample of GOF scores, was independent of the simulation and serves here as a generic set for the purpose of identifying the correlations that exist between the different metrics in Table \ref{tab:metrics}. As such, given the simulations for each velocity model (3), the components of motion (3), and the number of stations used in the validation (336) gives us a large enough sample of 3,024 GOF scores. Figure \ref{fig:data-box-plot} reinforces precisely this idea by comparing the statistical distribution of the broadband GOF scores of the simulations classified by velocity models and components. It is clear that although there are differences between them, these are minor and negligible; in other words, the statistical distribution of results for each metric is about the same independently of model or component.
